Application of Machine Learning to Increase the Efficiency of the Global Search Algorithm for Solving Multicriterial Problems\thanks{This research was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-10-17 2023/NUMTA/Full paper/NUMTA_2023_MCO.tex
fix two comments

If one or more partial criteria are not positive, this is not too restrictive, because it is possible to convert this problem to the statement satisfying conditions (\ref{eq:07}) with preserving the Pareto solution \cite{Pardalos2017}.

@@

>>>>

If one or more partial criteria are not positive, this is not too restrictive, because it is possible to convert this problem to the statement satisfying conditions (\ref{eq:07}) with preserving the Pareto solution. A substantiation for such a transformation is given, for example, in \cite{Pardalos2017}.

@@

\textbf{Remark}. The above method is based on the ISA  global search algorithm, which has an explicit geometric interpretation (see \cite{Strongin2000}). Using trial points, it is possible to design a minorant for the objective function $f(x)$. Then the value of characteristic, taken with the opposite sign, i.e. $-R(i)$, is the minimum value of the minorant in the interval $(x_{i-1}, x_i)$. Moreover, the point of a new trial $x^{p+1}$, computed according to (\ref{eq:26}), is carried out at the point, at which the minimum of the minorant is situated.
